Introduction

### 2025-11-19 Intro.Rmd
Added EDA visualizations and fixed knitting issues

```{r}
library(readr)
library(ggplot2)

@@

@@

```{r}
bank_train <- 
bank_test <- 
```

@@

bank_glm <- glm(y ~., data = bank_train, family = binomial)
summary(bank_glm)
```

@@

bank_lda <- lda(y ~., data = bank_full, subset = train)
bank_lda

bank_qda <- qda(y ~., data = bank_full, subset = train)
```

@@

## KNN

@@

bank_knn <- knn()
```

@@

Optimize K value (w.r.t cross validation tesst error)

@@

```{r}
library(gam)
bank_gam <- gam(y ~ , data = bank_train) # basis functions

>>>>

```{r}
library(readr)
library(ggplot2)
library(dplyr)
library(tidyr)

@@

# Calculate and print the success rate
success_rate <- mean(bank_full$y == "yes") * 100
cat("Overall Subscription Success Rate:", round(success_rate, 2), "%\n")

# bar plot for the target variable 'y'
ggplot(bank_full, aes(x = y, fill = y)) +
  geom_bar() +
  labs(title = "Distribution of Term Deposit Subscription (y)",
       x = "Subscribed to Term Deposit?",
       y = "Count") +
  theme_minimal()

# Convert variables to factors for plotting

bank_full$y <- as.factor(bank_full$y)
bank_full$job <- as.factor(bank_full$job)
bank_full$marital <- as.factor(bank_full$marital)
bank_full$education <- as.factor(bank_full$education)
bank_full$contact <- as.factor(bank_full$contact)
bank_full$month <- as.factor(bank_full$month)
bank_full$poutcome <- as.factor(bank_full$poutcome)
bank_full$housing <- as.factor(bank_full$housing)
bank_full$loan <- as.factor(bank_full$loan)

ggplot(bank_full, aes(x = job, fill = y)) +
  geom_bar(position = "fill") +
  coord_flip() +
  labs(title = "Subscription Rate by Job",
       y = "Proportion") +
  theme_minimal()

```{r}
ggplot(bank_full, aes(x = education, fill = y)) +
  geom_bar(position = "fill") +
  coord_flip() +
  labs(title = "Subscription Rate by Education Level",
       y = "Proportion") +
  theme_minimal()
```

ggplot(bank_full, aes(x = marital, fill = y)) +
  geom_bar(position = "fill") +
  coord_flip() +
  labs(title = "Subscription Rate by Marital Status",
       y = "Proportion") +
  theme_minimal()

```{r}
ggplot(bank_full, aes(x = contact, fill = y)) +
  geom_bar(position = "fill") +
  labs(title = "Subscription Rate by Contact Type",
       y = "Proportion") +
  theme_minimal()
```

```{r}
ggplot(bank_full, aes(x = poutcome, fill = y)) +
  geom_bar(position = "fill") +
  labs(title = "Subscription Rate by Previous Marketing Campaign Outcome",
       y = "Proportion") +
  theme_minimal()
```

```{r}
bank_full %>%
  group_by(campaign) %>%
  summarise(success_rate = mean(y == "yes")) %>%
  ggplot(aes(x = campaign, y = success_rate)) +
  geom_line() +
  geom_point() +
  labs(title = "Subscription Success Rate vs. Number of Campaign Contacts",
       x = "Number of Contacts During This Campaign",
       y = "Success Rate") +
  theme_minimal()
```

@@

```{r}
#bank_train <- 
#bank_test <- 
```

@@

#bank_glm <- glm(y ~., data = bank_train, family = binomial)
#summary(bank_glm)
```

@@

#bank_lda <- lda(y ~., data = bank_full, subset = train)
#bank_lda

#bank_qda <- qda(y ~., data = bank_full, subset = train)
```

@@

## KNN
Interpretable in a different way... Can be used to identify customers similar to those that are subscirbed.

@@

#bank_knn <- knn()
```

@@

Optimize K value (w.r.t cross validation test error)

@@

```{r}
library(gam)
#bank_gam <- gam(y ~ , data = bank_train) # basis functions
